\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage{multicol}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ashton du Plessis} % Your name
% You can merge both of these into a single line, if you do not have a website.
% \address{{060 974 2730} \\ {ashtondup@gmail.com}}
\address{\href{https://www.linkedin.com/in/ashton-du-plessis-00b7a6256/}{My LinkedIn} \\ \href{https://github.com/Ashtondup}{GitHub} \\ \href{https://ashtondup.github.io/AshtonduPlessisCV/}{Web CV}} %\\ \href{www.faangpath.com}{www.faangpath.com}} 

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{Objective}

{Software Engineer with development experience, seeking full-time Full-stack developer roles.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf National Senior Certificate}, Ermelo High School \hfill {2015 - 2019}% \\
% Subject choices were: Mathematics, Physical Science, Engineering Graphical and Design, and Computer Application Technologies. Was the best student in Computer Application Technologies in my grade for the year 2019.

{\bf Bachelor of Science in Information Technology}, North-West University, Potchefstroom Campus \hfill {2020 - 2023}

{\bf Bachelor of Science Honours in Computer Science and Information
Technology}, North-West University, Potchefstroom Campus \hfill {Expected 2024}\\
Relevant Coursework: Information Systems Engineering, Computer Security, Artificial Intelligence and Decision Support Systems.
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Coding Languages & Python, C++, C\#, .NET Framework, ASP.NET, Java, SQL, \LaTeX{}, HTML, CSS,\\
& JavaScript\\
Soft Skills & Problem-solving, Team work, Source control (GitHub), Project management
\end{tabular}
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Student Assistant} \hfill Mar 2023 - Jun 2023\\
North-West University \hfill \textit{Potchefstroom Campus}
\begin{itemize}
    \itemsep -3pt {} 
    \item Helped students with queries regarding C\#.
    \item Marked students C\# projects. 
\end{itemize}

\textbf{Vocational Work} \hfill 24 June 2024 - 5 July 2024\\
Synertech \hfill \textit{Lanseria}
\begin{itemize}
    \itemsep -3pt {} 
    \item 2 weeks of vacation work.
    \item Learned basic structure of a development team.
\end{itemize}

\textbf{Cybersecurity Challenge} \hfill 19 August 2024 - 30 August 2024\\
SANReN \hfill %\textit{Lanseria}
\begin{itemize}
    \itemsep -3pt {} 
    \item Learned how to revearsed engineer apk and .exe files.
    \item Learned about OSINT
    \item Waiting for results.
\end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{AI Fruit Classification.} {A group AI project for Honours AI module. Made in Python by making use of PyTorch, Torchvision, Kivy, Jupyter notebook, and Google Colab for training the model. This project can be found in my GitHub.}
\item \textbf{Chatbot.} {A basic chatbot made in C++. Takes preset input and can response to these preset input to one of three ways. This project can be found in my GitHub.}
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Personal Intrests} %{Extra-Curricular Activities} 
    \begin{multicols}{3}
        \begin{itemize}
            \item Puzzle solving.
            \item Raspberry Pi.
            \item Information security/Cybersecurity.
            \item Games
            \item Rock music
        \end{itemize}
        \end{multicols}


\end{rSection}

%----------------------------------------------------------------------------------------
% \begin{rSection}{Leadership} 
% \begin{itemize}
%     \item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
% \end{itemize}


% \end{rSection}


\end{document}
